Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-12-12 scagnostics.Rmd
Tentative Fig 4 to potentially replace Fig 3.

>>>>

## Tentative
try how this looks going first to V1 vs V5, then to V5 vs V6
```{r wIntermediatePath}
if(!file.exists("cache/wIntermediate.rda")){
  m1 <- matrix(c(1,0,0,0,0,0,0,1,0,0,0,0),ncol=2)
  mInt <- matrix(c(1,0,0,0,0,0,0,0,0,0,1,0),ncol=2)
  m2 <- matrix(c(0,0,0,0,1,0,0,0,0,0,0,1),ncol=2)
  #this is silly but seems that first two entries are being ignored, so need some fake entries
  m3 <- matrix(c(1,0,0,0,1,0,0,1,0,0,0,1),ncol=2)
  m4 <- matrix(c(1,1,1,0,0,0,0,1,1,0,0,0),ncol=2)
  t3 <- save_history(sin100,tour_path=planned_tour(list(m3,m4,m1,mInt,m2)))
  t3full <- as.list(interpolate(t3))
  fullResPlanned <- getProj(sin100, t3full, "sin", 100) %>%
    rbind(getProj(sin1000, t3full, "sin", 1000)) %>%
    rbind(getProj(spiral100, t3full, "spiral", 100)) %>%
    rbind(getProj(spiral1000, t3full, "spiral", 1000)) %>%
    rbind(getProj(pipe100, t3full, "pipe", 100)) %>%
    rbind(getProj(pipe1000, t3full, "pipe", 1000))
  save(t3, t3full, fullResPlanned, file = "cache/wIntermediate.rda")
} else {
  load("cache/wIntermediate.rda")
}
```

```{r wIntermediate, fig.width=6, fig.height=7, fig.cap="PPIs for projections along an interpolation between a nuisance and a structured projection (solid lines: $n=1000$; dashed: $n=100$). Most of the indexes have peaks at the end of the sequence, indicating that they see the structure. The scagnostics, MIC and TIC see all three structures, so are more flexible for general pattern detection."}
fullResMeltPlanned <- fullResPlanned %>%
  mutate(convex = 1-convex) %>% 
  rowwise() %>%
  mutate(holes = rescaleHoles(holes)) %>%
  gather(PPI, value, -t, -name, -size) %>%
  filter(PPI != "cmass") %>%
  mutate(PPI = fct_relevel(PPI, "holes", "convex", "skinny", "stringy", "dcor2d", "splines2d", "MIC", "TIC"))
fullResMeltPlanned %>% 
  ggplot(aes(x=t, y=value)) + 
  geom_line(aes(group=size, linetype=factor(size, levels=c("1000", "100")))) + 
  ylim(c(0,1)) +
  facet_grid(PPI~name) + 
  theme(legend.position="none") + xlab("Sequence of projections (t)") + ylab("PPI value")
```
